---
title: "The rational use of causal inference to guide reinforcement learning strengthens with age"
author: "AC & KN"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

<style type="text/css">

h1.title {
  font-size: 38px;
}
h1 { /* Header 1 */
  font-size: 28px;
}
h2 { /* Header 2 */
    font-size: 22px;
}
h3 { /* Header 3 */
  font-size: 18px;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r setDirs, echo = FALSE}
root <- rprojroot::find_rstudio_root_file() #find R project path
scriptDir <- file.path(root, 'Scripts/agencytask') #path to script directory
dataDir <- file.path(root, 'Data/agencyTask_data/Analyses') #path to data directory
setwd(scriptDir)
```

```{r loadPackages,echo = FALSE}
library(Rmisc)
library(ggplot2)
library(lme4)
library(lmerTest)
library(sjPlot)
library(car)
```

```{r loadData, echo=FALSE}
setwd(dataDir)
data <- read.csv("anonymized_mining_data.csv") #read in trialwise data
data$ageScaled <- scale(data$age) #scale age
data$ageScaledsq <- (data$ageScaled)^2 
data$subject <- as.factor(data$subject) #set subject as a factor
data$feedback <- as.factor(data$feedback) #set reward as a factor
data$condition <- as.factor(data$condition) #set condition as a factor
data$condition <- factor(data$condition, labels = c("Robber", "Millionaire", "Sheriff")) #change labels
data$condition <- factor(data$condition, levels = c("Millionaire", "Robber", "Sheriff")) #change order of levels
data$trial_in_blockScaled <- scale(data$trial_in_block) #scale trial number
data = data[!is.na(data$usable),] #remove subjects that did not meet accuracy criteria
data = droplevels(data)
```

# Main text analyses and figures

## Attribution model
```{r attributionModel, echo=FALSE}

#find whether age or age sq model is best
attributionmodelagelin <- glmer(latent_guess ~ feedback * condition * ageScaled +  (1|subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data) 

attributionmodelagesq <- glmer(latent_guess ~ feedback * condition * ageScaled + feedback * condition * ageScaledsq +  (1|subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data) 

anova(attributionmodelagelin,attributionmodelagesq)

options("contrasts")

#fit maximal model
attributionmodelagesqfbcondslopeint <- glmer(latent_guess ~ feedback * condition * ageScaled + feedback * condition * ageScaledsq + (feedback*condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(feedback = "contr.sum", condition = "contr.sum"), data = data) 

Anova(attributionmodelagesqfbcondslopeint, type = "III")

```

## Learning model
```{r learningModel, echo=FALSE}

#find whether age or age sq model is best
learningmodelagelin <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled + (1|subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data)

learningmodelagesq <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled + trial_in_blockScaled * condition * ageScaledsq + (1|subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data)

anova(learningmodelagelin,learningmodelagesq)

#fit maximal model
learningmodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled + trial_in_blockScaled * condition * ageScaledsq + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum"), data = data) 

Anova(learningmodelagesqcondtrialslopeint, type = "III")

```

## Plot attributions
```{r plotAttrib, echo=FALSE}

library(dplyr)

meanattrib = data %>%
                 group_by(subject,age,condition,feedback) %>%
                 summarise(meanlatent_guess = mean(latent_guess))

ggplot(meanattrib, aes(x=age, y=meanlatent_guess, colour=feedback, group=feedback)) +
  geom_point(size=2) +
  scale_colour_manual(breaks = c("0","1"), labels = c("Rocks","Gold"), values = c("darkgrey","gold1"), name = "Outcome") +
  scale_fill_manual(breaks = c("0","1"), labels = c("Rocks","Gold"), values = c("darkgrey","gold1"), guide = FALSE) +
  stat_smooth(method="glm",formula=y~poly(x,2), fullrange=TRUE, aes(fill=feedback)) +
  xlab("Age") + #x axis label
  ylab("Proportion attributed to agent") + #y axis label
  scale_y_continuous(expand = c(0,0), limits = c(-0.01,1.1)) +
  theme(title= element_text(size=26, face="bold"),
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black", vjust=0.6, angle = 60),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) + #diff pre-set themes available, or create your own
   facet_wrap(~condition) 
```

## Plot learning
```{r plotLearn, echo=FALSE}
#create 10 trial bins
data$bin <- ifelse(data$trial_in_block <= 10,"1", ifelse(data$trial_in_block > 10 & data$trial_in_block <= 20, "2", ifelse(data$trial_in_block > 20 & data$trial_in_block <= 30, "3", ifelse(data$trial_in_block > 30 & data$trial_in_block <= 40, "4", "5"))))
data$bin <- as.factor(data$bin)

meanlearnbin = data %>%
                    group_by(subject,age_group,condition,bin) %>%
                    summarise(meanoptchoice = mean(optimal_choice))

#generate summary stats for plotting
meanlearnbin.wstat = summarySE(meanlearnbin, measurevar= "meanoptchoice", groupvars=c("condition","bin","age_group"))
#reorder factors
meanlearnbin.wstat$age_group <- factor(meanlearnbin.wstat$age_group, levels = c("Kid","Teen","Adult"))
levels(meanlearnbin.wstat$age_group) <- c("Children", "Adolescents", "Adults")

ggplot(meanlearnbin.wstat, aes(x= bin, y=meanoptchoice, colour=condition)) +
  geom_point(size = 6, position= position_dodge(width=0.2), aes(colour=condition)) +
  geom_errorbar(aes(colour=condition, ymin=meanoptchoice-se, ymax=meanoptchoice+se),position = position_dodge(),width =.1, size=1.2)+
  scale_color_manual(breaks = c("Millionaire", "Robber", "Sheriff"), values = c("lightgreen","indianred1","lightblue3"), name = "Territory") +
  xlab("Binned trials (10 per bin)") +
  ylab("Proportion optimal choice") +
  geom_line(aes(group=condition, colour = condition), size=1.2) + #add a line connecting the dots
  geom_hline(aes(yintercept=0.5), linetype="dashed") + #add a dashed line at y = 0
theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black"),
        axis.text.y= element_text(size=22, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_wrap(~age_group) +
  ggtitle("Empirical Data")

```

## Make plots of simulated age group learning data
```{r plotACCblockbin, echo=FALSE}
setwd(dataDir)
#load full tidyverse
library(tidyverse)

#Read in simulated data
simDataRealParams <- read_csv("accTable_realParams_sims.txt")

#first just deal with accuracy
simAccDataRealParams <- simDataRealParams[c(1:9, 19:27, 37:45)]
simAccDataRealParams$bin <- 1:5

#Get in tidy format by gathering acc
tempRP <- gather(simAccDataRealParams, key = "condition", value = "acc", oneLR_robberAcc_adultSims, oneLR_millionaireAcc_adultSims, oneLR_sheriffAcc_adultSims, bayes_robberAcc_adultSims, bayes_millionaireAcc_adultSims, bayes_sheriffAcc_adultSims, bayesadapt_robberAcc_adultSims, bayesadapt_millionaireAcc_adultSims, bayesadapt_sheriffAcc_adultSims, oneLR_robberAcc_teenSims, oneLR_millionaireAcc_teenSims, oneLR_sheriffAcc_teenSims, bayes_robberAcc_teenSims, bayes_millionaireAcc_teenSims, bayes_sheriffAcc_teenSims, bayesadapt_robberAcc_teenSims, bayesadapt_millionaireAcc_teenSims, bayesadapt_sheriffAcc_teenSims, oneLR_robberAcc_kidSims, oneLR_millionaireAcc_kidSims, oneLR_sheriffAcc_kidSims, bayes_robberAcc_kidSims, bayes_millionaireAcc_kidSims, bayes_sheriffAcc_kidSims, bayesadapt_robberAcc_kidSims, bayesadapt_millionaireAcc_kidSims, bayesadapt_sheriffAcc_kidSims)

#separate condition column into multiple columns
temp2RP <- separate(tempRP, condition, into = c("Model", "Environment", "AgeGroup"), sep = "_")

#remove "acc" from factor name
temp3RP <- separate(temp2RP, Environment, into = c("Environment", "drop"), sep = "A") %>%
  select(-drop)

temp3RP <- separate(temp3RP, AgeGroup, into = c("AgeGroup", "drop"), sep = "S") %>%
  select(-drop)


simAccDataRealParams <- temp3RP

#Repeat for error
simErrorDataRealParams <- simDataRealParams[c(10:18, 28:36, 46:55)]

#gather error
tempRP <- gather(simErrorDataRealParams, key = "condition", value = "error", oneLR_robberAccErr_adultSims, oneLR_millionaireAccErr_adultSims, oneLR_sheriffAccErr_adultSims, bayes_robberAccErr_adultSims, bayes_millionaireAccErr_adultSims, bayes_sheriffAccErr_adultSims, bayesadapt_robberAccErr_adultSims, bayesadapt_millionaireAccErr_adultSims, bayesadapt_sheriffAccErr_adultSims, oneLR_robberAccErr_teenSims, oneLR_millionaireAccErr_teenSims, oneLR_sheriffAccErr_teenSims, bayes_robberAccErr_teenSims, bayes_millionaireAccErr_teenSims, bayes_sheriffAccErr_teenSims, bayesadapt_robberAccErr_teenSims, bayesadapt_millionaireAccErr_teenSims, bayesadapt_sheriffAccErr_teenSims, oneLR_robberAccErr_kidSims, oneLR_millionaireAccErr_kidSims, oneLR_sheriffAccErr_kidSims, bayes_robberAccErr_kidSims, bayes_millionaireAccErr_kidSims, bayes_sheriffAccErr_kidSims, bayesadapt_robberAccErr_kidSims, bayesadapt_millionaireAccErr_kidSims, bayesadapt_sheriffAccErr_kidSims)

#separate condition column into multiple columns
temp2RP <- separate(tempRP, condition, into = c("Model", "Environment", "AgeGroup"), sep = "_")

#remove "AccError" from factor name
temp3RP <- separate(temp2RP, Environment, into = c("Environment", "drop"), sep = "A") %>%
  select(-drop)

temp3RP <- separate(temp3RP, AgeGroup, into = c("AgeGroup", "drop"), sep = "S") %>%
  select(-drop)

simErrorDataRealParams <- temp3RP

#merge sim error data and sim acc data
simDataRealParams <- merge(simAccDataRealParams, simErrorDataRealParams, by = c("bin", "Environment", "Model", "AgeGroup"))

#reorder model factors
simDataRealParams$Model <- as.factor(simDataRealParams$Model) %>%
  fct_relevel("oneLR", "bayesadapt", "bayes")

simDataRealParams$AgeGroup <- as.factor(simDataRealParams$AgeGroup) %>%
  fct_relevel("kid", "teen", "adult")

simDataRealParams_oneLR <- subset(simDataRealParams, Model=="oneLR")
simDataRealParams_bayesadapt <- subset(simDataRealParams, Model=="bayesadapt")
simDataRealParams_bayes <- subset(simDataRealParams, Model=="bayes")

facet_names <- c('kid' = 'Children', 'teen' = 'Adolescents', 'adult' = 'Adults')

#plot
ggplot(simDataRealParams_oneLR, aes(x= bin, y=acc)) +
  geom_point(size = 6, position= position_dodge(width=0.2), aes(color=Environment)) +
  geom_errorbar(aes(color=Environment, ymin=acc-error, ymax=acc+error),position = position_dodge(),width =.1, size=1.2) +
  scale_color_manual(values = c("lightgreen","indianred1","lightblue3"), name = "Territory", breaks=c("millionaire", "robber", "sheriff"), labels=c("Millionaire", "Robber", "Sheriff")) +
  xlab("Binned trials (10 per bin)") +
  ylab("Proportion optimal choice") +
  scale_x_continuous(labels= c("1", "2", "3","4", "5"))   +
  geom_line(aes(group=Environment, colour = Environment), size=1.2) + #add a line connecting the dots
  geom_hline(aes(yintercept=0.5), linetype="dashed") + #add a dashed line at y = 0
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black"),
        axis.text.y= element_text(size=22, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(~ AgeGroup, labeller = as_labeller(facet_names)) +
  ggtitle("Simulated One Learning Rate Data")

ggplot(simDataRealParams_bayesadapt, aes(x= bin, y=acc)) +
  geom_point(size = 6, position= position_dodge(width=0.2), aes(color=Environment)) +
  geom_errorbar(aes(color=Environment, ymin=acc-error, ymax=acc+error),position = position_dodge(),width =.1, size=1.2) +
  scale_color_manual(values = c("lightgreen","indianred1","lightblue3"), name = "Territory", breaks=c("millionaire", "robber", "sheriff"), labels=c("Millionaire", "Robber", "Sheriff")) +
  xlab("Binned trials (10 per bin)") +
  ylab("Proportion optimal choice") +
  scale_x_continuous(labels= c("1", "2", "3","4", "5"))   +
  geom_line(aes(group=Environment, colour = Environment), size=1.2) + #add a line connecting the dots
  geom_hline(aes(yintercept=0.5), linetype="dashed") + #add a dashed line at y = 0
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black"),
        axis.text.y= element_text(size=22, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(~ AgeGroup, labeller = as_labeller(facet_names)) +
  ggtitle("Simulated Adaptive Bayesian Data")

ggplot(simDataRealParams_bayes, aes(x= bin, y=acc)) +
  geom_point(size = 6, position= position_dodge(width=0.2), aes(color=Environment)) +
  geom_errorbar(aes(color=Environment, ymin=acc-error, ymax=acc+error),position = position_dodge(),width =.1, size=1.2) +
  scale_color_manual(values = c("lightgreen","indianred1","lightblue3"), name = "Territory", breaks=c("millionaire", "robber", "sheriff"), labels=c("Millionaire", "Robber", "Sheriff")) +
  xlab("Binned trials (10 per bin)") +
  ylab("Proportion optimal choice") +
  scale_x_continuous(labels= c("1", "2", "3","4", "5"))   +
  geom_line(aes(group=Environment, colour = Environment), size=1.2) + #add a line connecting the dots
  geom_hline(aes(yintercept=0.5), linetype="dashed") + #add a dashed line at y = 0
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black"),
        axis.text.y= element_text(size=22, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(~ AgeGroup, labeller = as_labeller(facet_names)) +
  ggtitle("Simulated Empirical Bayesian Data")

```

# Supplementary Information

## Attribution model w effect of trial
```{r attributiontrialModel, echo=FALSE}

data$trial_numScaled <- scale(data$trial_num)

attributionmodelagesqfbcondslopeintwtrial <- glmer(latent_guess ~ feedback * condition * ageScaled + feedback * condition * ageScaledsq + trial_numScaled + (feedback*condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(feedback = "contr.sum", condition = "contr.sum"), data = data)

Anova(attributionmodelagesqfbcondslopeintwtrial, type = "III")

attributionmodelagesqfbcondslopeintwtrialint <- glmer(latent_guess ~ feedback * condition * ageScaled * trial_numScaled + feedback * condition * ageScaledsq * trial_numScaled + (feedback*condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(feedback = "contr.sum", condition = "contr.sum"), data = data) #does not converge

```

## Territory order analysis

```{r condorderModels, echo=FALSE}
#First conditions
#Version A = Robber 
#Version B = Millionaire
#Version C = Sheriff
#Version D = Robber
#Version E = Millionaire
#Version F = Sheriff

data$firstcondition <- ifelse(data$version == "A" | data$version == "D" | data$version == "d","Robber", ifelse(data$version == "b" | data$version == "B" | data$version == "E", "Millionaire", "Sheriff"))

data$firstcondition <- as.factor(data$firstcondition)

learningCondOrdermodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled +  trial_in_blockScaled * condition * ageScaledsq + firstcondition + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum", firstcondition = "contr.sum"), data = data) #converges

Anova(learningCondOrdermodelagesqcondtrialslopeint, type = "III")

data$version[data$version == "b"] <- "B"
data$version[data$version == "c"] <- "C"
data$version[data$version == "d"] <- "D"

data <- droplevels(data)

learningversionmodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled +  trial_in_blockScaled * condition * ageScaledsq + version + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum", version = "contr.sum"), data = data) #convergea

Anova(learningversionmodelagesqcondtrialslopeint, type = "III")
```

## Learning generalization analysis

```{r generalizModel, echo=FALSE}

data$block <- as.factor(data$block_num)

#learninggeneralizmodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled * block * firstcondition +  trial_in_blockScaled * condition * ageScaledsq * block * firstcondition + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum", block = "contr.sum", firstcondition = "contr.sum" ), data = data) #does not converge

#learninggeneralizmodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled +  trial_in_blockScaled * condition * ageScaledsq + block * firstcondition + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum", block = "contr.sum", firstcondition = "contr.sum" ), data = data) #does not converge

learninggeneralizmodelagesqcondtrialslopeint <- glmer(optimal_choice ~ trial_in_blockScaled * condition * ageScaled +  trial_in_blockScaled * condition * ageScaledsq + block + firstcondition + (trial_in_blockScaled * condition||subject), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum", block = "contr.sum", firstcondition = "contr.sum" ), data = data) #converges

Anova(learninggeneralizmodelagesqcondtrialslopeint , type = "III")


meanlearngenbin = data %>%
                    group_by(subject, bin, block) %>%
                    summarise(meanoptchoice = mean(optimal_choice))

#generate summary stats for plotting
meanlearngenbin.wstat = summarySE(meanlearngenbin, measurevar= "meanoptchoice", groupvars=c("bin", "block"))

ggplot(meanlearngenbin.wstat, aes(x= bin, y=meanoptchoice, colour=block)) +
  geom_point(size = 6, position= position_dodge(width=0.2), aes(colour=block)) +
  geom_errorbar(aes(colour=block, ymin=meanoptchoice-se, ymax=meanoptchoice+se),position = position_dodge(),width =.1, size=1.2)+
  xlab("Binned trials (10 per bin)") +
  ylab("Proportion optimal choice") +
  geom_line(aes(group=block, colour = block), size=1.2) + #add a line connecting the dots
  geom_hline(aes(yintercept=0.5), linetype="dashed") + #add a dashed line at y = 0
theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=22, colour="black"),
        axis.text.y= element_text(size=22, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) 

```

## RT analyses
```{r RTmodels, echo=FALSE}

data$choiceRTlog <- log(data$choice_RT)
data$trial_numScaled <- scale(data$trial_num)

learningRTmodelagelin <- lmer(choiceRTlog ~ trial_numScaled * condition * ageScaled + (1|subject), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data)

learningRTmodelagesq <- lmer(choiceRTlog ~ trial_numScaled * condition * ageScaled +  trial_numScaled * condition * ageScaledsq + (1|subject), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = data)

anova(learningRTmodelagelin,learningRTmodelagesq) #age-sq model preferred

learningRTmodelagesqcondtrialslopeint <- lmer(choiceRTlog ~ trial_numScaled * condition * ageScaled +  trial_numScaled * condition * ageScaledsq + (trial_numScaled * condition||subject), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(condition = "contr.sum"), data = data) 

Anova(learningRTmodelagesqcondtrialslopeint, type = "III")
```

## Plots of RT model effects
```{r plotchoidRTModel, echo=FALSE}
plot_model(learningRTmodelagesqcondtrialslopeint, type = "pred", terms = c("trial_numScaled")) +
    ylab("Log transformed reaction times") +
  xlab("Trial number") +
  scale_x_continuous(breaks = c(-1.720461, 0, 1.721216), labels = c(1,75,150)) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black"),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +#diff pre-set themes available, or create your own
  ggtitle("Predicted Probabilities")

plot_model(learningRTmodelagesqcondtrialslopeint, type = "pred", terms = c("ageScaled")) +
    ylab("Log transformed reaction times") +
  xlab("Age") +
  scale_x_continuous(breaks = c(-1.676, 0.0392, 1.727), labels = c(7,16,25)) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26, vjust=-0.5),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black"),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +#diff pre-set themes available, or create your own
  ggtitle("Predicted Probabilities")

```